Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-27 Paper/MSRChallenge2017.tex

It is also worth noting that the Kappa statistic increases in both cases when
adding social data (100\% and 85\% respectively). The Kappa statistic is a measurement that also accounts for the accuracy of the predicting power of the model. Furthermore, Kappa is a more 
robust measure than \textit{correctly classified} instances, since it takes into account the
correctly guessed instances occurring by chance. The mean absolute error also
decreases in both cases, which provides further evidences that social factors
are important when predicting build success.

>>>>

It is also worth noting that the Kappa statistic increases in both cases when
adding social data (100\% and 85\% respectively). The Kappa statistic is a measurement that also accounts for the accuracy of the predicting power of the model. Furthermore, Kappa is a more 
robust measure than \textit{correctly classified} instances, since it takes into account the
correctly guessed instances occurring by chance. The precision, recall and F-measure are calculated over the successful and unsuccessful classes and then averaged (standard procedure in Weka). Precision and recall are calculated as follows:

\begingroup
    \fontsize{9pt}{12pt}\selectfont
Precision = True Positives / (True Positives + False Positives)\

Recall = True Positives / (True Positives + False Negatives)
\endgroup

F-score is a correlation of these two values. We can see that all these measures increase when we add social data into the feature space, making the prediction more reliable. Besides this, the mean absolute error
decreases in both cases, which provides further evidences that social factors
are important when predicting build success.
